\documentclass[12pt]{article}
\usepackage{fullpage,enumitem,amsmath,amssymb,graphicx}
\usepackage{algorithm}
\begin{document}

\begin{center}
{\Large CS221 Fall 2015 Homework 3}

\begin{tabular}{rl}
SUNet ID: & lguan \\
Name: & Leying Guan \\
\end{tabular}
\end{center}

By turning in this assignment, I agree by the Stanford honor code and declare
that all of this is my own work.

\section*{Problem 1}

\begin{enumerate}[label=(\alph*)]
  \item It won't work if buy picking a sub-optimal for earlier word, we could
decrease cost dramatically later because our goal is to find the global optimal.
Here is a concrete example: rainyday.

Suppose we have the following unigram cost dictionary:

\{day: 1, rain:2, rainy:3\}

the word ``rain'''s cost is 2 but ``rainy'''s cost is 3. The greedy
algorithm will give us ``rain yday'' but the optimal solution is ``rainy day''. 
\item Code
\end{enumerate}
\section*{Problem 2}

\begin{enumerate}[label=(\alph*)]
\item The fundamental reason is the same as problem 1-- local optimal is not
equal to global optimal in this case, and here is a example I give:

possible files:\{ht:(hat, hot, hate); dg:(dog, dag) \}

bigramcost dictionay: \{my hat: 1 ; may hot:10; hot dog:1; hate dog:2 \}

input:my ht dg

The greedy algorithm will give us ``my hat dog'' while the global optimal is
``my hot dog''.
\item Code
\end{enumerate}

\section*{Problem 3}

\begin{enumerate}[label=(\alph*)]
  \item The states consist of sets of two elements: (location, previou word) where
location indicates where should the next search start and previou word is the
word right before this successors' seach.

The actions consist of choices we take for next move, which is the new word we
consider.

The costs consist of bigramCost(previous word, new word).

The initial state is (0, start of sentence) which means we are at the begining
of the sentence and ready to start.

The end state is (n, last word) where n is the length of input string.

\item Code

\item Define $u_b(w) = \min_{w'} b(w', w)$, then this unigram cost is consistent
because $\forall s$, we have
\begin{align*}
Cost(s, a) &= \min_{v_1,...,v_K}\sum^K_{k = 2} b(v_1, v_k)\\
& \leq \min_{v_1,...,v_K}\sum^K_{k = 1} u_b(v_k)\\
& = Cost'(s,a)
\end{align*}
By definition, h is a consistent heuristic.
\end{enumerate}

\end{document}
